Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-06-29 kappa.tex
Add paleo-timeseries plot from original data.

% Text label over graphics
% from http://tex.stackexchange.com/questions/128844/put-subfigure-labels-
% inside-figures-using-subfig-package
\newcommand{\subgraphics}[3][,]{%
  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
  \leavevmode\rlap{\usebox1}% Print image
  \rlap{\hspace*{0.25em}
        \raisebox{\dimexpr\ht1-3ex}{\textbf{(#2)}}}% Print label
  \phantom{\usebox1}% Insert appropriate spacing
  \hspace{1cm}% Add horizontal separator
}

@@

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-glacier-crevasses}
    \subgraphics{b}{photo-glacier-fold}
  }
  \caption{Different mechanical behaviours of glacier ice.
           \textbf{(a)} Brittle behaviour. Ice flowing over a hidden bedrock
           knob, resulting in fracturing at the glacier surface.
           Glacier Blanc, French Alps.
           \textbf{(b)} Ductile behaviour. Mountain glacier calving into a
           small lake, revealing a folded structure formed by deformed rock
           layers in the ice.}
  \label{fig:glacier-mechanics}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics[width=50mm]{a}{photo-glacial-valley}
    \subgraphics[width=50mm]{b}{photo-erratic-boulder}
    \subgraphics[width=50mm]{c}{photo-melt-channels}
  }
  \caption{Different indicators of past glaciation.
           \textbf{(a)} Glacial valley, exhibiting a broad, U-shaped profile
           characteristic of erosion by glaciers.
           Cirque du Fer-\`{a}-Cheval, French Alps.
           \textbf{(b)} Erratic boulders, deposited in an improbable
           arrangement as the glacier melted underneath.
           Finse area, Norwegian Scandes.
           \textbf{(c)} Lateral meltwater channels, formed on a gentle slope
           as the ice margin retreated towards the valley bottom. Tuya Lake
           area, Canadian Cordillera.}
  \label{fig:glaciation-indicators}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-timeseries}
  \caption{The oxygen isotope record from oceanic sediments is a proxy for ice
           volume on land during Earth's hitory. Over the last million years,
           it shows predominance of a 100\,ka cycle of glacial and
           interglacial periods. This thesis focuses on the last glacial cycle.
           \todo{This figure is directly from \citet{Lisiecki.Raymo.2005}.
           Redraw it using the data they provide.}}
  \label{fig:palaeo-timeseries}
\end{figure}

>>>>

% Text label over graphics
% from http://tex.stackexchange.com/questions/128844/put-subfigure-labels-
% inside-figures-using-subfig-package
\newcommand{\subgraphics}[3][,]{%
  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
  \leavevmode\rlap{\usebox1}% Print image
  \rlap{\hspace*{0.25em}
        \raisebox{\dimexpr\ht1-3ex}{\textbf{(#2)}}}% Print label
  \phantom{\usebox1}% Insert appropriate spacing
}

@@

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-glacier-crevasses}
    \hspace{1cm}
    \subgraphics{b}{photo-glacier-fold}
  }
  \caption{Different mechanical behaviours of glacier ice.
           \textbf{(a)} Brittle behaviour. Ice flowing over a hidden bedrock
           knob, resulting in fracturing at the glacier surface.
           Glacier Blanc, French Alps.
           \textbf{(b)} Ductile behaviour. Mountain glacier calving into a
           small lake, revealing a folded structure formed by deformed rock
           layers in the ice.}
  \label{fig:glacier-mechanics}
\end{figure}

@@

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics[width=50mm]{a}{photo-glacial-valley}
    \hspace{1cm}
    \subgraphics[width=50mm]{b}{photo-erratic-boulder}
    \hspace{1cm}
    \subgraphics[width=50mm]{c}{photo-melt-channels}
  }
  \caption{Different indicators of past glaciation.
           \textbf{(a)} Glacial valley, exhibiting a broad, U-shaped profile
           characteristic of erosion by glaciers.
           Cirque du Fer-\`{a}-Cheval, French Alps.
           \textbf{(b)} Erratic boulders, deposited in an improbable
           arrangement as the glacier melted underneath.
           Finse area, Norwegian Scandes.
           \textbf{(c)} Lateral meltwater channels, formed on a gentle slope
           as the ice margin retreated towards the valley bottom. Tuya Lake
           area, Canadian Cordillera.}
  \label{fig:glaciation-indicators}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-timeseries}
  \caption{Indicators of climatic fluctuations during the last 800\,ka of
           Earth history.
           \textbf{(a)} Benthic oxygen isotope \chem{\delta^{18}O} record from
           a compilation of globally-distributed oceanic sediment cores
           \citep{Lisiecki.Raymo.2005}. Higher \chem{\delta^{18}O} values
           correspond to periods of lower temperatures of the deep ocean, or
           of lower global sea level, and thus higher ice volume stored in
           glaciers and ice sheets on land.
           \textbf{(b)} Temperature anomalies reconstructed from a central
           Antarctic ice core \citep[EPICA,][]{Jouzel.etal.2007}.
           The grey boxes indicate the approximate time span of the last
           glacial period of 110 to 10\,ka, which corresponds to our period of
           interest in the present thesis.}
  \label{fig:palaeo-timeseries}
\end{figure}
